---
title: "Weight of Fish"
author: "Connor Rice"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
fullupPerch <- lm(Weight~ .,data=Perch)
summary.lm(fullupPerch)
```
```{r}
PerchMODL1 <- lm(Weight~ .-Length2,data=Perch)
summary.lm(PerchMODL1)
```
```{r}
PerchMODL2 <- lm(Weight~ .-Length2-Length1,data=Perch)
summary.lm(PerchMODL2)
```

```{r}
PerchMODL3 <- lm(Weight~ .-Length2-Length1-Length3,data=Perch)
summary.lm(PerchMODL3)
```
## PerchMODL3 Best model??
```{r}
PerchMODL4 <- lm(Weight~ .-Length2-Length1-Length3-Width,data=Perch)
summary.lm(PerchMODL4)
```

### Best Models

### Best Two regressor model


## Pike


```{r}
fullupPike <- lm(Weight~ .,data=Pike)
summary.lm(fullupPike)
```

## fullupPike Best model??

```{r}
PikeMODL1 <- lm(Weight~ .-Length2,data=Pike)
summary.lm(PikeMODL1)
```
```{r}
PikeMODL2 <- lm(Weight~ .-Length2-Length1,data=Pike)
summary.lm(PikeMODL2)
```
```{r}
PikeMODL3 <- lm(Weight~ .-Length2-Length1-Length3,data=Pike)
summary.lm(PikeMODL3)
```
```{r}
PikeMODL4 <- lm(Weight~ .-Length2-Length1-Length3-Width,data=Pike)
summary.lm(PikeMODL4)
```

### Best Models

### Best Two regressor model

## Roach

```{r}
fullupRoach <- lm(Weight~ .,data=Roach)
summary.lm(fullupRoach)
```
```{r}
RoachMODL1 <- lm(Weight~ .-Length2,data=Roach)
summary.lm(RoachMODL1)
```
```{r}
RoachMODL2 <- lm(Weight~ .-Length2-Length1,data=Roach)
summary.lm(RoachMODL2)
```
```{r}
RoachMODL3 <- lm(Weight~ .-Length2-Length1-Length3,data=Roach)
summary.lm(RoachMODL3)
```
```{r}
RoachMODL4 <- lm(Weight~ .-Length2-Length1-Length3-Height,data=Roach)
summary.lm(RoachMODL4)
```

## RoachMODL4 Best model??

### Best Models

### Best Two regressor model

## Final Summary Statements